\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-27 paper.tex
WIP Conclusion + formatting

\uwds is a distributed and lightweight framework that enables robot programmers
to build and refine in real-time spatial and temporal models of the environment
surrounding a robot. \uwds make it possible to share these world models amongst
the software components running on the robot. Critically, \uwds permits to
represent and manipulate in a distributed manner \emph{multiple alternatives} to
the current, perceived world model: for instance, the world with some objects filtered out,
the world `viewed' from the perspective of another agent, an hypothetical world
resulting from the simulated application of a plan, etc.

@@

As mentioned in section~\ref{arch}, \uwds uses Google's gRPC as message passing
protocol. The protocol is explicitely defined (using the \emph{protocol
buffers}\footnote{\url{https://developers.google.com/protocol-buffers/}}
interface definition language), and bindings to various languages
and platforms can be automatically generated from the protocol definition file
(as of Feb 2017, gRPC can generate bindings for C, C++, C\#, Node.js, PHP, Ruby,
Python, Go and Java on Windows, Mac and Linux).

@@

\end{pythoncode}
    \caption{Example of a simple yet complete \uwds filter, written in Python, and named {\tt
    walls\_filter}: the client connects to the \uwds network, walkthrough the
    scene graph of world {\tt example\_in}, filter out some objects, and publish
    the remaining objects in the world {\tt example\_out}.}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-photo2}
    \caption{A user manipulating objects on RFID mat while an operator monitors the interaction via an {\tt uwds view} client}
    \label{fig|l2torexample}
\end{figure}
\uwds has been used within the European L2TOR project~\cite{belpaeme2015l2tor} in order to conceptualize and visualize the spatial relations and visibility of the physical objects that users interact with. In one of the scenarios of this project, users are instructed by a NAO robot to manipulate a number of Duplo-like animals on top of a printed background paper which serves as a landscape (See \ref{fig|l2torexample}). The robot instructions are based on pedagogical strategies to promote spatial relation learning by object manipulation. Such instructions include commands like to place the elephant \textit{on top} or \textit{next to} the cube or put the giraffe \textit{inside} the house.
For that reason, the robot and the operator should be able to access whether the user performs the required task and at the same time envisage their perspective. A number of \uwds clients have been developed in order to provide a distributed model of the environment and the robot as described in the next section.

@@

The scenario consists of a number of \uwds clients distributed accross two computers that communicate with each other in order to provide an updated representation of the world. Figure \ref{fig|l2torarchitecture} illustrates the high level communication of the \uwds clients that form the achitecture of the L2TOR spatial relations platform.\\
\\L2TOR \uwds clients:
\subsubsection{Kinect Head Tracker} {Captures the location and the direction of the user's head - Camera point}
\subsubsection{Object RFID tracker} {Updates the locations of the virtual objects based on RFID data}
\subsubsection{NAO model}{Virtual representation of the Robot - Camera poit}
\subsubsection{Visibility computation}{Computes visibility based on camera points}
\subsubsection{Spatial Relations computation}{Extracts spatial relations between the virtual objects}
\subsubsection{Game/Rules computation}{Interaction manager based on \uwds clients' input}

The L2TOR project features an additional scenario where the user performs the manipulations on a tablet computer instead of using physical objects. To accomodate this change, we replaced the object detection \uwds client with a 3D virtual object detection while the rest of the system remains the same. Finally, we are evaluating the use of a hybrid platform that utilizes both virtual and physical objects at the same time.

@@

>>>>

\uwds is a distributed and lightweight open-source
framework\footnote{\url{https://github.com/severin-lemaignan/underworlds}} that
enables robot programmers to build and refine in real-time spatial and temporal
models of the environment surrounding a robot. \uwds make it possible to share
these world models amongst the software components running on the robot.
Critically, \uwds permits to represent and manipulate in a distributed manner
\emph{multiple alternatives} to the current, perceived world model: for
instance, the world with some objects filtered out, the world `viewed' from the
perspective of another agent, an hypothetical world resulting from the simulated
application of a plan, etc.

@@

As mentioned in section~\ref{arch}, \uwds uses Google's gRPC as message passing
protocol. The protocol is explicitly defined (using the \emph{protocol
buffers}\footnote{\url{https://developers.google.com/protocol-buffers/}}
interface definition language), and bindings to various languages
and platforms can be automatically generated from the protocol definition file
(as of Feb 2017, gRPC can generate bindings for C, C++, C\#, Node.js, PHP, Ruby,
Python, Go and Java on Windows, Mac and Linux).

@@

\end{pythoncode}
    \caption{Example of a simple yet complete \uwds filter, written in Python, and named {\tt
    walls\_filter}: the client connects to the \uwds network, walk through the
    scene graph of world {\tt example\_in}, filter out some objects, and publish
    the remaining objects in the world {\tt example\_out}.}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-photo2}
    \caption{A user manipulating objects on RFID mat while an operator monitors
    the interaction via an {\tt uwds view} client}

    \label{fig|l2torexample}
\end{figure}

\uwds has been used within the European L2TOR project~\cite{belpaeme2015l2tor}
in order to conceptualize and visualize the spatial relations and visibility of
the physical objects that users interact with. In one of the scenarios of this
project, users are instructed by a NAO robot to manipulate a number of
Duplo-like animals on top of a printed background paper which serves as a
landscape (See \ref{fig|l2torexample}). The robot instructions are based on
pedagogical strategies to promote spatial relation learning by object
manipulation. Such instructions include commands like to place the elephant
\textit{on top} or \textit{next to} the cube or put the giraffe \textit{inside}
the house.  For that reason, the robot and the operator should be able to access
whether the user performs the required task and at the same time envisage their
perspective. A number of \uwds clients have been developed in order to provide a
distributed model of the environment and the robot as described in the next
section.

@@

The scenario consists of a number of \uwds clients distributed across two
computers that communicate with each other in order to provide an updated
representation of the world. Figure \ref{fig|l2torarchitecture} illustrates the
high level communication of the \uwds clients that form the architecture of the
L2TOR spatial relations platform.

L2TOR \uwds clients:

\begin{itemize}
    \item \textbf{Kinect Head Tracker} Captures the location and the direction
        of the user's head - Camera point

    \item \textbf{Object RFID tracker} Updates the locations of the virtual
        objects based on RFID data

    \item \textbf{NAO model} Virtual representation of the Robot - Camera poit

    \item \textbf{Visibility computation} Computes visibility based on camera
        points

    \item \textbf{Spatial Relations computation} Extracts spatial relations
        between the virtual objects

    \item \textbf{Game/Rules computation} Interaction manager based on \uwds
        clients' input

\end{itemize}

The L2TOR project features an additional scenario where the user performs the
manipulations on a tablet computer instead of using physical objects. To
accommodate this change, we replaced the object detection \uwds client with a 3D
virtual object detection while the rest of the system remains the same. Finally,
we are evaluating the use of a hybrid platform that utilizes both virtual and
physical objects at the same time.

@@

We have introduced \uwds, a novel framework for shared and composable
spatio-temporal representations of a robot's world. The key contributions of our
approach are: a composite data-structure for environment representation within a
robotic software architecture, made of a scene graph and a timeline; a mechanism
to efficiently and transparently share this data-structure amongst a set of
clients (the software modules of the robot); a cascading architecture permitting
the explicit of representation of alternative states of the world while
maintaining a network of dependencies amongst themselves; a typology of clients
(\emph{root}, \emph{leaf}, \emph{filter}, \emph{transformer}) to systematically
describe such a network of representations dependencies.

We have presented as well a concrete instantiation of a system relying on \uwds
for its representation needs, and we have sketched future directions of
development.
